\begin{abstract}
Industrial Control Systems (ICS) used in manufacturing, power generators
and other critical infrastructure monitoring and control are  ripe targets for cyber attacks
these days. Examples of such attacks are abundant such as attacks on Iranian nuclear enrichment plant with Stuxnet in 2009,
on German steel plant in 2014, Ukrainian power system in 2015 and 2016 etc.
 Usually in ICS, multiple control loops work concurrently and share various resources including
communication bus through which they interact with sensors and actuators. The
real-time scheduling of concurrent control applications while competing for shared 
resources, is done with delicate balance between performance and real-time constraints.
A possible insider attack could be the replacement of a previously vetted control application 
or other software components in the system,
during a system update.  In this paper, we
propose an automated framework that addresses the effect of such 
code replacement attacks from the perspective of loss of control
performance. Given a set of control components, a control
objective to be satisfied by the control ensemble, the question
of schedulability and synthesis of a scheduler that can ensure
the desired control performance has been recently studied in the 
literature. In this paper, we extend this idea further to 
build an automata theoretic framework for assessment of code
replacement attacks on schedulability. We have built an end-to-end framework that takes in a set of control components,
their variants (after code replacement), a control objective
to be guaranteed, and performs an automated schedulability
assessment. We report some preliminary experiments of our
framework on simple benchmarks.

\end{abstract}

\begin{IEEEkeywords}
 CyberPhysical System, \textcolor{black}{Cooperative Control}, \textcolor{black}{Code Replacement Attack}, 
 \textcolor{black}{Insider threat},  $\omega$-regular language, B\"{u}chi Automaton, Schedulability
\end{IEEEkeywords}