\section{Introduction} \label{sec:intro}
\noindent
Most critical infrastructures such as power grid, water / sewage control, power generation plants, industrial automation etc., are cyber-physical systems (CPS). Cyber-Physical systems have two major interacting components -- a component with physical dynamics governed by laws of physics -- modeled with partial differential equations, another component -- control, computing and networking which controls the physical dynamics. For very large and geographically distributed cyber physical systems, the control trajectory is designed to be stable and reliable with very complex distributed as well as centralized control. The control components today 
routinely involve a non-trivial amount of software, running on embedded control units on-board, to support and run any moderately sophisticated CPS infrastructure. \\

\noindent
In recent history, cyber physical systems have been a popular victim of choice for so called cyber attacks, the effects of which have been moderate to as ravaging as blackouts~\cite{blackout} or financial loss. This has prompted 
NIST~\cite{nist} to promote cyber security frameworks for critical infrastructure~\cite{cs-Framewrok} as 
one of the themes of immediate research attention. Given that no cyber security framework is full proof, significant research thrust is being invested in recent times to develop techniques that allow us to continually monitor the physical dynamics of these systems and look for any anomalies that could be indicative of cyber attack induced problems. Early detection of system dynamics changes would allow us to contain the damage by immediately islanding parts of the system which seem to be the origin areas in the infrastructure. \\

\noindent
Research investment in security of CPS is 
extremely crucial for developing novel technology for cyber attack detection, prevention, and countermeasures. \textcolor{black} {Systematic} studies on different sources of cyber attacks have revealed myriads of possibilities by which these cyber threats can 
propagate inside a CPS infrastructure. A popular and widely acknowledged means of cyber-attack, {\em phishing attacks}, originate when someone whose desktop
is connected to the control network opens an email containing a payload, which can then
take over the control of the business network, and in turn the control network. However, since
much of the cyber threat models also assume insider knowledge or sabotage, even an isolated
control network is not devoid of cyber-attack possibilities. A popular example  is the notorious Sony Pictures hack~\cite{SonyHack2014} which leaked a release of confidential data from the film studio Sony Pictures. A person with local or remote access
to the equipment of the physical plant, or access to the various interfaces such as programmable
logic controllers (PLCs) or other Intelligent Electronic Device (IEDs) that are connected to the
physical system for measurements and control can exploit a vulnerability in these devices to
induce an attack on the system. One could also gain access to the control network, and create
various kinds of man-in-the-middle attacks by either suppressing measurements or control
actuation signals, replaying stale measurements or actuation signals, or even injecting
maliciously planned false data. These kinds of attacks would then mislead the controllers, and
wrong control actions could lead to disastrous industrial accidents. One could also hack into the
controllers or the various other computing elements in the control center such as the process control servers by
exploiting some vulnerabilities in their design and attack the cyber physical system. In fact, in
case of the Stuxnet worm~\cite{stuxnet}, \textcolor{black} {vulnerabilities} in the Siemens SCADA system were exploited. While individual areas of cyber security research have received
much attention in academia (e.g. cryptography; crypto-analysis; network
security in the form of firewall and other perimeter security techniques, and intrusion detection, anti-virus software, and static analysis of software to detect vulnerabilities and zero-day attacks;
hardware Trojan detection), much of these research focus on guarding IT systems in business and corporate information infrastructure. \\ 

\noindent
{\bf Problem addressed in this paper:} The focus of study in this paper is code replacement attacks, wherein some or parts of a control component 
are compromised by tampering their operational modality 
by modifying the software running inside. 
Code replacement \cite{GhoshHD12} by internal employees, phishing attacks or other means of code injection
have been known to be a vector for cyber-attacks for a while. Stuxnet analysis showed that such
attacks were part of the repertoire in that case. In an industrial control environment with real time control components, code replacement can lead to disaster, for example, slowing down a
particular process in the industrial manufacturing can cascade a chain of failures in the whole
assembly line. In this paper, we propose an idea that will demonstrate that such
attacks for real-time SCADA systems can be guarded against by statically analyzing the
legitimate control programs, and constructing an omega-regular language based timing signature,
which can then be periodically checked on the running components to distinguish a replaced
component from the original component. The timing signature analysis of omega-regular languages was originally proposed by researchers in \cite{WeissFAA09}, in the context of real-time communication scheduling
in SCADA systems. \\

\noindent
{\bf Contributions of this work:}
In this paper, we address the problem of detecting code replacement attacks. Given a set of control components, a control objective 
to be satisfied by the control ensemble, the question of schedulability and 
synthesis of a scheduler that can ensure the desired control performance has been recently studied in literature~\cite{WeissFAA09, AlurW08, GhoshMDHD16}. 
In this paper, we extend the same philosophy to build an automata theoretic framework for assessment of code replacement attacks on schedulability. The foundation of our attack analysis framework is based on the notion of infinite automata-based reasoning of control performance and schedulability analysis, as illustrated in the following section. Automata theoretic modeling frameworks have been quite popular in literature for a wide variety of applications. Additionally, the power of finite automata over infinite words (B\"{u}chi automatons in particular) have been exploited in recent literature in control performance and stability analysis. Our work is another step in the same direction for assessing the effect of code replacement attacks in cyber-physical control. \\

\noindent
The idea of automata based control scheduling has been discussed in \cite{WeissA07}. They express
the communication interface among the control components using a formal language. This work illustrates how the interfaces of discrete-time switched linear systems
can be expressed using a B\"{u}chi automaton. Authors in \cite{AlurW08}  describe CPU scheduling
in terms of finite machines over infinite words. The infinite words depict the particular time 
slot for which a particular resource can be allotted to a specific control component. The work in \cite{WeissFAA09} applies automata based scheduling on networks, to formalize the effect of bus scheduling and network stability. Further, \cite{GhoshMDHD16} describes how the interfacing among 
the control actions can be modeled by B\"{u}chi automaton to guarantee stable and reliable
scheduling. This work presents a methodology for construction of a scheduler automata 
where each state represents one particular control schedule while generating the permissible 
schedule in terms of a $\omega$-regular language. Our work is an application framework based on the contributions above, with specific focus to code replacement attack and schedulability analysis. While one of the major control objectives discussed in the above contributions has been exponential stability, which we assume to be satisfied for individual control components, we propose to use a fairness schedule in our work, that requires a different modeling strategy, as explained in the following. More importantly, our work here can be considered as an end-to-end framework on automata-based control performance modeling and assessment. \\

\noindent
{\bf Organization:} This paper is organized as follows. Section \ref{sec3} describes the problem definition for this work along with a motivating example. Section \ref{sec4} presents the solution architecture. Section \ref{sec5} presents an overview of the tool we have developed. Section \ref{sec7} concludes this discussion.
