\section{Related Work} \label{sec2}
Replacement attacks \cite{GhoshHD12} carried out by internal employees, phishing attacks, code injection attacks have been known to be a vector for cyber-attacks for a while. Stuxnet analysis showed that such
attacks were part of the repertoire in that case. 
The idea of automata based control scheduling has been discussed in \cite{WeissA07}. They express
the communication interface among the control components using a formal language. This work illustrates how the interfaces of discrete-time switched linear systems
can be expressed using a B\"{u}chi automaton. Authors in \cite{AlurW08}  describe CPU scheduling
in terms of finite machines over infinite words. The infinite words depict the particular time 
slot for which a particular resource can be allotted to a specific control component. The work in \cite{WeissFAA09} applies automata based scheduling on networks, to formalize the effect of bus scheduling and network stability. Further, \cite{GhoshMDHD16} describes how the interfacing among 
the control actions can be modeled by B\"{u}chi automata to guarantee stable and reliable
scheduling. This work presents a methodology for construction of a scheduler automata 
where each state represents one particular control schedule while generating the permissible 
schedule in terms of a $\omega$-regular language. Our work is an application framework based on the contributions above, with specific focus to component replacement attacks and schedulability analysis. While one of the major control objectives discussed in the above contributions has been exponential stability, which we assume to be satisfied for individual control components, we propose to use a fairness schedule in our work, that requires a different modeling strategy, as explained in the following. More importantly, our work here can be considered as an end-to-end framework on automata-based control performance modeling and assessment. \\
